Non-exclusive Characteriazations of Demands and Resources across O*NET Job Elements

### 2024-12-30 Submission.Rmd
Updated manuscript per reviewer feedback

Data were collected through Prolific, an online data collection platform. An email was sent to **a random subset???** of all "eligible" members of the Prolific respondent pool, notifying them of their opportunity to participate. Eligibility requirements **included??** being 18 or older and holding either a full-time or part-time job. Eligible individuals then voluntarily chose whether or not to respond to the invitation after reading an informed consent.

Participants were asked to think about their primary job, and each administered survey branched content dependent on whether or not the respondent's job could be described as consisting of **98???** different O\*Net job characteristics. For example, if a respondent indicated that any one characteristic **was not** applicable for their job, they were not subsequently asked to rate the level of resource (...this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (...this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (...this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order. Participants were compensated six USD for their participation (the estimated time commitment pre-administration was 45 minutes).

@@

Similarly, hindrance demands and resources explained a statistically significant amount of the variability in burnout, $R^2$ = `r round(summary(hr_burn_m2)$r.squared, 2)`, Adj. $R^2$ =  `r round(summary(hr_burn_m2)$adj.r.squared, 2)`, `r hr_burn_info2$statistic$modelfit$r2`. The inclusion of the interaction term in step two of the model contributed a significant addition to the model, `r hr_burn_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r hr_burn_r_square_change`, $\Delta F$ (`r hr_burn_anova$Df[2]`, `r hr_burn_anova$Res.Df[2]`) = `r hr_burn_anova$F[2]`, supporting the presence of a moderated effect [see Figure \@ref(fig:hind-resource-burn-int)]. As expected, the relationship between hindrance demands and burnout becomes weaker as workers perceive more resources. Summatively these findings provide support for the assertion that resources would moderate the relationships between hindrance demands and the outcomes of strain and burnout.

>>>>

Data were collected through Prolific, an online data collection platform. An email was sent to eligible members of the Prolific respondent pool, notifying them of their opportunity to participate. Eligibility requirements included being 18 or older and holding either a full-time or part-time job. Eligible individuals then voluntarily chose whether or not to respond to the invitation after reading an informed consent.

Participants were asked to think about their primary job, and each administered survey branched content dependent on whether or not the respondent's job could be described as consisting of 98 different O\*Net job characteristics. For example, if a respondent indicated that any one characteristic was not applicable for their job (e.g., answered *never* or *not at all*), they were not subsequently asked to rate the level of resource (...this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (...this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (...this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order. Participants were compensated six USD for their participation (the estimated time commitment pre-administration was 45 minutes).

@@

Similarly, hindrance demands and resources explained a statistically significant amount of the variability in burnout, $R^2$ = `r round(summary(hr_burn_m2)$r.squared, 2)`, Adj. $R^2$ =  `r round(summary(hr_burn_m2)$adj.r.squared, 2)`, `r hr_burn_info2$statistic$modelfit$r2`. The inclusion of the interaction term in step two of the model contributed a significant addition to the model, `r hr_burn_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r hr_burn_r_square_change`, $\Delta F$ (`r hr_burn_anova$Df[2]`, `r hr_burn_anova$Res.Df[2]`) = `r hr_burn_anova$F[2]`, supporting the presence of a moderated effect (see Figure \@ref(fig:hind-resource-burn-int)). As expected, the relationship between hindrance demands and burnout becomes weaker as workers perceive more resources. Summatively these findings provide support for the assertion that resources would moderate the relationships between hindrance demands and the outcomes of strain and burnout.

### 2024-12-30 Submission.tex
Updated manuscript per reviewer feedback

Data were collected through Prolific, an online data collection platform. An email was sent to \textbf{a random subset???} of all ``eligible'' members of the Prolific respondent pool, notifying them of their opportunity to participate. Eligibility requirements \textbf{included??} being 18 or older and holding either a full-time or part-time job. Eligible individuals then voluntarily chose whether or not to respond to the invitation after reading an informed consent.

Participants were asked to think about their primary job, and each administered survey branched content dependent on whether or not the respondent's job could be described as consisting of \textbf{98???} different O*Net job characteristics. For example, if a respondent indicated that any one characteristic \textbf{was not} applicable for their job, they were not subsequently asked to rate the level of resource (\ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (\ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (\ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order. Participants were compensated six USD for their participation (the estimated time commitment pre-administration was 45 minutes).

>>>>

Data were collected through Prolific, an online data collection platform. An email was sent to eligible members of the Prolific respondent pool, notifying them of their opportunity to participate. Eligibility requirements included being 18 or older and holding either a full-time or part-time job. Eligible individuals then voluntarily chose whether or not to respond to the invitation after reading an informed consent.

Participants were asked to think about their primary job, and each administered survey branched content dependent on whether or not the respondent's job could be described as consisting of 98 different O*Net job characteristics. For example, if a respondent indicated that any one characteristic was not applicable for their job (e.g., answered \emph{never} or \emph{not at all}), they were not subsequently asked to rate the level of resource (\ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (\ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (\ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order. Participants were compensated six USD for their participation (the estimated time commitment pre-administration was 45 minutes).
